---
title: "stockEvaluator"
author: "Brandon Sie"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
      code_folding: hide
      toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libs}



```


```{r}

source("SE-functions.R")
libcallStocks()

# -- -- -- -- -- -- -- -- -- --
# Data Setup
# -- -- -- -- -- -- -- -- -- --

# Get Data
sym <- "AAPL"

today <- Sys.Date()
mindate <- ymd(today)-150


df <- getfdata(sym)

# (!) change Peroidicity


#add EMAs
df$EMA200 <- EMA(df$Close, 200)
df$EMA50 <- EMA(df$Close, 50)

# Technical Analysis (!) add PPO/others?


ta.bbands <- getbbands(fdata) # EMA Bollinger Bands


ta.macd <- getmacd(fdata) #MACD
macd.crossdate <- df$Date[df$crossMACD == TRUE] %>% last
macd.cross <- data.frame(Date = macd.crossdate,
								Value = df$macd[df$Date == macd.crossdate],
								Dir = df$macd_dir[df$Date == macd.crossdate])
# ta.candle <- getcandlestick(fdata)

#(!) rename bbands and macd variables etc

# (!) identify Crossovers


# join and subset data
df <- cbind(fdata,ta.bbands,ta.macd)  



# taplot(df)

#(!) set standardized month tickmarks

g1 <- 
	ggplot(df %>% subset(Date >= mindate), 
			 aes(x = Date, open = Open, high = High, low = Low, close = Close)) + 
	scale_x_bd(business.dates = df$Date) +	ylab("USD") + 
	theme(legend.position = "none") +
	
	# Bollinger Bands
	geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightskyblue2" , alpha = 0.3) + 
	geom_line(aes(y = mavg), color = "dodgerblue4") + 
	
	# EMAs
	geom_line(aes(y = EMA200), size = 1) + 
	geom_line(aes(y = EMA50), size = 1, color = "gray45") +
	
	# Barchart
	geom_candlestick() 
	
g2 <- 
	ggplot(df %>% subset(Date >= mindate),
				 aes(x = Date)) +	scale_x_bd(business.dates = df$Date) +	ylab("USD") + 
	theme(legend.position = "none") +
	
	#MACD
	geom_line(aes(y = macd)) +
	geom_line(aes(y = signal), size = 1) +
	# geom_vline(xintercept = last.cross.macd)
	geom_point(aes(x = macd.cross$Date, y = macd.cross$Value,
						 size = 3), color = ifelse(macd.cross$Dir == "Up", "green4", "red4"))
	


# https://cran.r-project.org/web/packages/egg/vignettes/Ecosystem.html
library(grid)
library(gtable)

g1 %<>% ggplotGrob
g2 %<>% ggplotGrobg <- rbind(g1,g2, size = "first")
grid.newpage()
grid.draw(g)


```


```{r}
library(robinhoodr)

hd_daily <- rh_historicals(symbols = "GOOG", 
                           interval = "10minute", 
                           span = "week", 
                           bounds = "regular", 
                           to_xts = FALSE)



```


ToDO
robinhood integration
for each ticker intraday, daily, two day, weekly, monthly charts
for each chart, last crossover date +_ direction
correlations

use PPO not mACD  ppo = macd / longer moving average (12 and 26 day?)
get stochastic oscillator stoch()
and derivative oscillator (based on rsi)
highlight graph when all are positive


add vertical line for crossovers
increase contrast bollinger band colors
add week/month etc




add long/short signals based oncrossover
https://www.r-bloggers.com/an-example-of-a-trading-strategy-coded-in-r/


# Add Volume Barchart Subplot
#second y axis https://plot.ly/r/multiple-axes/


  
# plotv <- df %>%
# 	  plot_ly(x=~Date, y=~Volume, type='bar', name = "Volume",
# 	          color = ~direction, colors = c('#d34141','#26cf17')) %>%
# 	  layout(yaxis = list(title = "Volume"),
# 	  			 title = "Stock", yaxis = "ym1")

#%>%
  # layout(yaxis = list(title = "Volume"),
  # 			 title = "Stock")


## Notes
http://rpubs.com/anishjoy1982/324594
http://www.rpubs.com/tdwbiz/85228
https://cran.r-project.org/web/packages/stocks/index.html
https://rpubs.com/Felix/6653
https://www.quantmod.com/examples/charting/#variants

technical indicators list
https://www.quantmod.com/examples/charting/#variants
?TA
newTa custom

documentation chartseries
https://www.rdocumentation.org/packages/quantmod/versions/0.4-13/topics/chartSeries

look into highcharts interactive




https://plot.ly/r/candlestick-charts/
https://plot.ly/r/graphing-multiple-chart-types/
